%%% Curriculum Vitae
%%% Author: William Gardner <wmgardn@gmail.com>
%%% Template author: Kieran Healy <kjhealy@gmail.com>
%%%
%%% ------------------------------------------------------------------------
%%% Requirements that are included in a modern tex distribution:
%%% ------------------------------------------------------------------------
%%% xelatex
%%% fontspec.sty
%%% hyperrref.sty
%%% xunicode.sty
%%% color.sty
%%% url.sty
%%% fancyhdr.sty
%%% memoir.cls
%%% fontawesome.sty
%%%
%%% ------------------------------------------------------------------------
%%% Requirements from https://github.com/kjhealy/latex-custom-kjh
%%% ------------------------------------------------------------------------
%%% org-preamble-xelatex.sty
%%% memoir-article-styles.sty
%%%
%%% ------------------------------------------------------------------------
%%% Optional
%%% ------------------------------------------------------------------------
%%% git
%%% vc.sty
%%% revnum.sty
%%% Fonts
%%%------------------------------------------------------------------------

\documentclass[11pt,article,oneside]{memoir}
\usepackage{org-preamble-xelatex}
\usepackage{fontawesome,url}
\usepackage{fontspec}
\usepackage[left=1.5in,
            right=1in,
            top=0.75in,
            bottom=0.75in]{geometry}


%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

\def\myauthor{William Gardner}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\myaffiliation{Columbia University Vagelos Colleges of Physicians & Surgeons}
\def\myemail{wmg2114@cumc.columbia.edu}
\def\myweb{willgardner.io}
\def\mygithub{github.com/willmgardner}
\def\mygooglescholar{Google Scholar}
\def\mytwitter{@willmgardner}

%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

%% Choose fonts for use with xelatex
%% Minion and Myriad are widely available, from Adobe.
\setromanfont[Mapping={tex-text},
	Numbers={OldStyle},
	Ligatures={Common}]{Minion Pro}
\setsansfont[Mapping=tex-text,
	Ligatures={Common},
	Colour=0033aa]{Unit-Medium}
\setmonofont[Mapping=tex-text,Scale=0.72]{Consolas}

\newfontface\scheader[SmallCapsFont={Minion Pro},SmallCapsFeatures={Letters=SmallCaps}]{Minion Pro}

\newfontfamily{\minbold}{Minion Pro Bold}[Scale=MatchUppercase]

\newfontface\addressblock[Mapping={tex-text},
	Numbers={OldStyle},
	Ligatures={Common}]{Minion Pro Medium Caption}

%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}


%% [optional] custom ampersand (font consistent with the one chosen above)
% \newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Minion Pro Medium}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~}

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{3.5in}
 \flushright {\footnotesize
 \href{http://healthdata.org}{Institute for Health Metrics and Evaluation} \\ University of Washington \\ 
 \vspace{.25 cm} \href{http://vagelos.columbia.edu}{Vagelos College of Physicians and Surgeons} \\ Columbia University \\}
\end{minipage}
\hfill
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.5in}
  \flushright \footnotesize {\texttt{\href{http://willgardner.io}{\myweb}} \, \faGlobe} \\
	{\texttt{\href{http://twitter.com/willmgardner}{\mytwitter}} \, \faTwitter}  \\
	{\texttt{\href{http://github.com/willmgardner}{\mygithub}} \, \faGithub} \\
  	{\texttt{\href{https://scholar.google.com/citations?user=LbtdQcsAAAAJ&hl=en&oi=ao}{\mygooglescholar}} \, \faGoogle} \\
  	{\texttt{\href{mailto:\myemail}{\myemail}} \, \faEnvelope} \\
\end{minipage}

\thispagestyle{empty}

\bigskip

%% Name
\noindent{\LARGE\scheader \textsc{william gardner}}
\reversemarginpar

\bigskip

%% Education

\marginhead{\sffamily {{\vskip -0.23em} education}}

\noindent{\minbold{Columbia University \vspace{0.01in}}}

\ind Doctor of Medicine, expected 2026.

\medskip
\noindent{\minbold{University of Washington \vspace{0.01in}}}

\ind MPH, Global Health Metrics, 2020.

\ind \hspace{0.35in} \footnotesize Thesis: \href{https://www.proquest.com/openview/e41ccfd9cef6b7376c1218dc0080b575/1?pq-origsite=gscholar&cbl=18750&diss=y}{\emph{Global, Regional, and National Estimates of Complete Coverage of Maternal \newline Obstetric Care
	Interventions, 1990--2019}}.\normalsize 

\medskip
\noindent{\minbold{Harvard University\vspace{0.01in}}}

\ind AB, Sociology, \emph{Magna cum laude} with Highest Honors, 2017.

\ind \hspace{0.35in} \footnotesize Thesis: \emph{Institutions, Inequalities, and Infant Death: Understanding the Role of Health Care \newline
Decommodification in Latin America} \newline Minor: Global Health and Health Policy \normalsize \vspace{0.01in}

\bigskip

%% Experience
\marginhead{\sffamily {{\vskip -0.23em} experience}}

% IHME
\noindent{\minbold{Institute for Health Metrics and Evaluation\vspace{0.01in}}} \hfill Seattle, WA

\ind Research Scientist \hfill 2020 -- present

\ind Post-Bachelor Fellow\vspace{0.02in} \hfill 2017 -- 2020

{\noindent \footnotesize Work on the Maternal and Child Health team as part of the Global Burden of Disease Study; Model disease
burden due to neonatal infectious diseases, distribution of population hemoglobin levels and prevalence of
anemia, burden of disease attributable to lead exposure and suboptimal breastfeeding, and a variety of
maternal and child health interventions, including coverage of antenatal care, skilled birth attendance,
caesarean section, and postnatal care.}

\bigskip

% Harvard Sociology
\noindent{\minbold{Department of Sociology, Harvard University\vspace{0.01in}}} \hfill Cambridge, MA

\ind Research Assistant\vspace{0.02in} \hfill 2015 -- 2017

{\noindent \footnotesize Worked under the direction of Professor Jason Beckfield on a project researching the effects of income
inequality on population health in Latin America using cross-national economic and health data from the
World Income Inequality Database, World Bank, and World Values Survey.}

\bigskip

% Cordeiro Summer Research Fellowship
\noindent{\minbold{Department of Global Health and Health Policy, Harvard University\vspace{0.01in}}} \hfill Cambridge, MA

\ind Cordeiro Summer Research Fellow\vspace{0.02in} \hfill 2016

{\noindent \footnotesize Conducted research for individual project entitled "Evaluating Distributional Effects of the Welfare State on
Health in Latin America," which culminated in my senior thesis; Duties included performing extensive
literature reviews and cited reference searches, acquiring and cleaning relevant data sources, data modeling
and statistical analysis, and manuscript writing.}

\bigskip

% Child Family Health International
\noindent{\minbold{Child Family Health International\vspace{0.01in}}} \hfill Quito \& Chone, Ecuador

\ind Urban and Rural Comparative Health Intern\vspace{0.02in} \hfill 2014

{\noindent \footnotesize Observed and participated in clinical rotations in various specialty clinics and hospitals in the towns of Quito
and Chone, Ecuador; Researched and reported on topics dealing with health disparities and inequalities between urban and rural healthcare systems; 
attended weekly lectures on topics in global health and health policy in Ecuador.}

\newpage

%% Publications
\marginhead{\sffamily {\vskip 0.35em} publications}
\medskip

\noindent\emph{Journal articles \vspace{0.05in}}

%% Use revnumerate environment if numbered publications are needed.
%% (Include it above in the preamble).
%% \renewcommand{\labelenumi}{\textsc{a}\theenumi.}
%% \begin{revnumerate}

\ind {\minbold Gardner WM}, GBD 2021 Anaemia Collaborators. Prevalence, years lived with disability, and trends in anaemia burden by severity 
and cause from 1990--2021: findings from the Global Burden of Disease Study 2021. Forthcoming in \emph{The Lancet Haematology.}

\ind GBD 2021 Sickle Cell Disease Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S2352-3026(23)00118-7}{Global, regional, and national prevalence and mortality burden of sickle cell disease, 2000--2021: 
a systematic analysis from the Global Burden of Disease Study 2021}. \emph{The Lancet Haematology} 2023. Advance online publication.

\ind GBD 2019 Healthcare Access and Quality Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S2214-109X(22)00429-6}{Assessing performance of
the Healthcare Access and Quality Index, overall and by select age groups, for 204 countries and territories,
1990--2019: a systematic analysis from the Global Burden of Disease Study 2019}. \emph{The Lancet Global Health} 2022; 10: e1715--43.

\ind GBD 2019 LRI Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S1473-3099(22)00510-2}{Age-sex differences in the global burden of lower
respiratory infections and risk factors, 1990--2019: results from the Global Burden of Disease Study 2019}. \emph{The Lancet Infectious Diseases} 2022; 22: 1626--47.

\ind Gonçalves BP, Procter SR, Paul P, Chandna J, \emph{et al. (including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S2214-109X(22)00093-6}{Group B streptococcus infection during pregnancy 
and infancy: estimates of regional and global burden}. \emph{The Lancet Global Health} 2022; 10: e807--19.

\ind Fitzgerald R, Manguerra H, Arndt MB, {\minbold Gardner WM}, \emph{et al.} \href{https://doi.org/10.1126/sciadv.abm8954}{Current dichotomous metrics obscure trends in
severe and extreme child growth failure}. \emph{Science Advances} 2021; 8.

\ind GBD 2019 Under-5 Mortality Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S0140-6736(21)01207-1}{Global, regional, and national progress
towards Sustainable Development Goal 3.2 for neonatal and child health: all-cause and cause-specific
mortality findings from the Global Burden of Disease Study 2019}. \emph{The Lancet} 2021; 398: 870--905.

\ind Local Burden of Disease Exclusive Breastfeeding Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1038/s41562-021-01108-6}{Mapping inequalities
in exclusive breastfeeding in low- and middle-income countries, 2000--2018}. \emph{Nature Human Behaviour} 2021; 5: 1027--45.

\ind GBD 2019 Universal Health Coverage Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S0140-6736(20)30750-9}{Measuring universal health
coverage based on an index of effective coverage of health services in 204 countries and territories, 1990--2019: a 
systematic analysis for the Global Burden of Disease Study 2019}. \emph{The Lancet} 2020; 396: 1250--84.

\ind GBD 2019 Risk Factors Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S0140-6736(20)30752-2}{Global burden of 87 risk factors in 204
countries and territories, 1990--2019: a systematic analysis for the Global Burden of Disease Study 2019}. \emph{The Lancet} 2020; 396: 1223--49.

\ind GBD 2019 Diseases and Injuries Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S0140-6736(20)30925-9}{Global burden of 369 diseases and
injuries in 204 countries and territories, 1990--2019: a systematic analysis for the Global Burden of Disease
Study 2019}. \emph{The Lancet} 2020; 396: 1204--22.

\ind GBD 2019 Viewpoint Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S0140-6736(20)31404-5}{Five insights from the Global Burden of Disease Study 2019}. 
\emph{The Lancet} 2020; 396: 1135--59.

\ind India State-Level Disease Burden Initiative Child Mortality Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S0140-6736(20)30471-2}{Subnational mapping of under-5 and neonatal mortality trends in India: the Global Burden of Disease Study
2000--17}. \emph{The Lancet} 2020; 395: 1640--58.

\ind GBD 2017 Lower Respiratory Infections Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S1473-3099(19)30410-4}{Quantifying risks and interventions that have affected
the burden of lower respiratory infections among children younger than 5 years: an analysis for the Global
Burden of Disease Study 2017}. \emph{The Lancet Infectious Diseases} 2020; 20: 60--79.

\newpage

\ind GBD 2017 Diarrhoeal Disease Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S1473-3099(19)30401-3}{Quantifying risks and interventions that have
affected the burden of diarrhoea among children younger than 5 years: an analysis of the Global Burden of
Disease Study 2017}. \emph{The Lancet Infectious Diseases} 2020; 20: 37--59.

\ind India State-Level Disease Burden Initiative Malnutrition Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S2352-4642(19)30273-1}{The burden
of child and maternal malnutrition and trends in its indicators in the states of India: the Global Burden of
Disease Study 1990--2017}. \emph{The Lancet Child \& Adolescent Health} 2019; 3: 855--70.

\ind Bhattacharjee N, Schaeffer L, Marczak L, Ross J, Swartz S, Albright J, {\minbold Gardner WM}, Shields C, \emph{et al.} 
\href{https://doi.org/10.1038/s41591-019-0525-0}{Mapping exclusive breastfeeding in Africa between 2000 and 2017}. \emph{Nature Medicine} 2019; 25: 1205--12.

\ind GBD 2017 SDG Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S0140-6736(18)32281-5}{Measuring progress from 1990 to 2017 and
projecting attainment to 2030 of the health-related Sustainable Development Goals for 195 countries and
territories: a systematic analysis for the Global Burden of Disease Study 2017}. \emph{The Lancet} 2018; 392: 2091--138.

\ind GBD 2017 Risk Factor Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S0140-6736(18)32225-6}{Global, regional, and national comparative
risk assessment of 84 behavioural, environmental and occupational, and metabolic risks or clusters of risks
for 195 countries and territories, 1990--2017: a systematic analysis for the Global Burden of Disease Study
2017}. \emph{The Lancet} 2018; 392: 1923--94.

\ind GBD 2017 Disease and Injury Incidence and Prevalence Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S0140-6736(18)32279-7}{Global, regional, and national incidence,
prevalence, and years lived with disability for 354 diseases and injuries for 195 countries and territories, 1990--2017: a 
systematic analysis for the Global Burden of Disease Study 2017}. \emph{The Lancet} 2018; 392: 1789--858.

\ind GBD 2017 DALYs and HALE Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S0140-6736(18)32335-3}{Global, regional, and national disability-adjusted
life-years (DALYs) for 359 diseases and injuries and healthy life expectancy (HALE) for 195 countries and
territories, 1990--2017: a systematic analysis for the Global Burden of Disease Study 2017}. \emph{The Lancet} 2018; 392: 1859--922.

\ind GBD 2017 Causes of Death Collaborators \emph{(including \textbf{Gardner WM}).} \href{https://doi.org/10.1016/S0140-6736(18)32203-7}{Global, regional, and national age-sex-specific
mortality for 282 causes of death in 195 countries and territories, 1980--2017: a systematic analysis for the
Global Burden of Disease Study 2017}. \emph{The Lancet} 2018; 392: 1736--88.

%\end{revnumerate}
%\newpage
\bigskip

\marginhead{\sffamily {\vskip 0.5em} conference \newline presentations}
\medskip

\ind {\minbold Gardner WM} and Kassebaum NJ. \href{https://doi.org/10.1093/cdn/nzaa053_035}{"Global, Regional, and National Prevalence of Anemia and Its
Causes in 204 Countries and Territories, 1990--2019."} American Society for Nutrition Annual Conference, 2020. (Finalist for Emerging 
Leaders in Nutrition Science Award))

\ind {\minbold Gardner WM} and Kassebaum NJ. \href{https://doi.org/10.1093/cdn/nzaa054_064}{"Global, Regional, and National Prevalence and Trends in Infant Breastfeeding Status in 204 Countries and Territories, 1990--2019."} 
American Society for Nutrition Annual Conference, 2020.

\ind {\minbold Gardner WM} and Kassebaum NJ. "Global, Regional, and National Coverage of Maternal Care
Interventions." Society for Pediatric and Perinatal Epidemiology Annual Conference, 2020. 

\bigskip

\marginhead{\sffamily {\vskip 0.5em} professional \newline organizations}
\medskip

\ind Society for Pediatric and Perinatal Epidemiology \hfill 2019 -- present

\ind American Society for Nutrition \hfill 2019 -- present

\ind WHO scientific advisory group for \emph{Group B Streptococcus} vaccine value proposition \hfill 2019 -- 2022

\bigskip

\marginhead{\sffamily {\vskip 0.6em}honors \newline \& awards}
\medskip

\ind Emerging Leaders in Nutrition Science Award, American Society for Nutrition (finalist) \hfill 2020

\ind Phi Beta Kappa \hfill 2017

\ind David McCord Prize (Harvard University) \hfill 2017

\ind John Harvard Scholar \hfill 2016 -- 2017

\ind Cordeiro Health Policy Summer Research Fellowship \hfill 2016

\bigskip

\end{document}
